\section*{Abstract}
Stock price movements reveal such a complex nature that identifying their causes is impossible to fully address. Many previous studies incorporate external factors such as news articles in order to show their impact on price movements for use cases like prediction models. In this work, it is proposed to incorporate the business relationship among companies in order to understand the similar evolution of their stock prices. To this end, stock prices for 467 components of the S\&P~500 market index are extensively processed by statistical and econometric methods to subsequently calculate their cross-correlation among each other. Further, representative features for business relationships are extracted from financial news from Reuters and Bloomberg. The conclusive correlation analysis between both emerging features, stock price similarity and business relationship, reveals evidence for a significant connection. The results suggest that stock prices should not be examined separately but rather related stock prices should be modelled collectively. Concluding, graph models should be used more intensively in order to provide a better understanding what factors have an impact on price changes.

% Stock prices reveal an impenetrable nature when it comes to identifying causes for price movements.

% The objective of this work is to explain stock prices by incorporating the relationship among stock prices.

% This work is an effort to put more emphasis on relation between companies in order to ...

% The rather emotional decisions of investors are susceptible to a plethora of factors such as political tension, media reporting and social media.

% traded on the American Exchanges NYSE and NASDAQ



% https://www.sfu.ca/~jcnesbit/HowToWriteAbstract.htm
% 1. Near the beginning, state the research question
% 2. What is the goal
% 3. Set accurate expectations
% 4, here should be one or more sentences assigned to summarize each chapter.
% 5. do not tell readers what you did, but what you discovered.
% 6. Approximately the last half of the abstract should be dedicated to summarizing and interpreting your results.


% Constraints
% Who reads it
% 150 words
% The structure of the abstract should mirror the structure of the whole thesis, and should represent all its major elements.
% stand-alone text
% substituting for the whole thesis when there is insufficient time and space for the full text.


% Examples:
% "The results suggest that the
% predictability of a financial market and the feasibility of profitable model-based trading are
% significantly influenced by the maturity of the market, the forecasting method employed, the
% horizon for which it generates predictions and the methodology used to assess the model and
% simulate model-based trading. We also find evidence against the informational value of
% indicators from the field of technical analysis. Overall, we confirm that advanced forecasting
% methods can be used to predict price changes in some financial markets and we discuss
% whether these results question the prevailing view in the financial economics literature that
% financial markets are efficient"

% "respectively. Experiments on the data collected from stock market in Mainland China show that the"